---
title: "Impactful_VisualizationCH"
author: "Valentin Henriot"
date: "01/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
library(WDI)
```

## Unemployment comparison between Switzerland, France, Germany and Italy

```{r Unemployment with advanced education comparison, include=FALSE}
UAEcomparison<- WDI(indicator = "SL.UEM.ADVN.ZS", #Unemployment with advanced education (% of total labor force with advanced education)
country = c("CH", "DE", "FRA", "IT"),
                   start = 2000,
                   end = 2018)
UAEcomparison
```

```{r Renaming column Advanced_Education comparison, include=FALSE}
base::colnames(UAEcomparison)[colnames(UAEcomparison)=="SL.UEM.ADVN.ZS"] <- "Advanced_EducationC"
UAEcomparison
```

```{r Unemployment intermediate education comparison, include=FALSE}
UIEcomparison<- WDI(indicator = "SL.UEM.INTM.ZS", #Unemployment with intermediate education (% of total labor force with advanced education)
country = c("CH", "DE", "FRA", "IT"),
                   start = 2000,
                   end = 2018)
UIEcomparison
```

```{r Renaming column Intermediate_Education comparison, include=FALSE}
base::colnames(UIEcomparison)[colnames(UIEcomparison)=="SL.UEM.INTM.ZS"] <- "Intermediate_EducationC"
UIEcomparison
```

```{r Unemployment basic education comparison, include=FALSE}
UBEcomparison <- WDI(indicator = "SL.UEM.BASC.ZS", #Unemployment with basic education (% of total labor force with advanced education)
country = c("CH", "DE", "FRA", "IT"),
                   start = 2000,
                   end = 2018)
UBEcomparison
```

```{r Renaming column Basic_Education comparison, include=FALSE}
base::colnames(UBEcomparison)[colnames(UBEcomparison)=="SL.UEM.BASC.ZS"] <- "Basic_EducationC"
UBEcomparison
```

```{r Combining columns comparison, include=FALSE}
library(dplyr)
UCjoin <- bind_cols(UAEcomparison, UIEcomparison, UBEcomparison)
UCjoin
```

```{r Delete some columns comparison, include=FALSE}
UCjoin$iso2c <- NULL
UCjoin$iso2c1 <- NULL
UCjoin$country1 <- NULL
UCjoin$year1 <- NULL
UCjoin$iso2c2 <- NULL
UCjoin$country2 <- NULL
UCjoin$year2 <- NULL
UCjoin
```

```{r Re-arrange columns comparison, include=FALSE}
UCjoin <- UCjoin[c(1,3,2,4,5)]
UCjoin
```

```{r Gather data about unemployment comparison, include=FALSE}
library(tidyr)

UCjoinTest <- gather(data = UCjoin, key = TYPE, value = VAL, Advanced_EducationC, Intermediate_EducationC, Basic_EducationC)
```

```{r Graphic about unemployment rate by education level comparison}
library(ggplot2)
qplot(data = UCjoinTest, y = VAL, x = year, color = TYPE, geom = "line") + 
  labs(y = "Unemployment rate in %", title = "Unemployment rate by education level") +
  facet_wrap(~ country) +
  theme_linedraw()
```

## Conclusion of the comparison

As we can see from the graph, *Switzerland* has had a relatively stable unemployment rate since the early 2000s. An increase of about **2.2% in 18 years for those with a high or intermediate level of education** and an increase of about **3.8% for those with a low level of education**.
Only *Germany* is doing better than *Switzerland* in terms of unemployment at the end of 2018 for those with a high or intermediate level of education. Nevertheless, the gap remains small, **1.6% for the advanced education category** and **1.9% for the intermediate level**. *Switzerland* is doing better than *Germany* in terms of employability in the low education category, with a **0.7% gap** in favour of *Switzerland*.

In contrast, *France and Italy* are the worst performers, with unemployment rates for all education categories combined far higher than *Germany and Switzerland*. 
For example, the unemployment rate for the low and intermediate education categories is **twice as high** in *France* as in *Switzerland* in 2018.
*Italy* shows similar results to *France*.

Finally, it is interesting to note that *Germany* has seen its **unemployment rate fall since 2005**, *Switzerland* remains **stable**, while *France and Italy* have seen their **unemployment rates rise since 2006**, although there has been a **slight improvement over the last 5 years**.