---
title: "Country Report Switzerland"
author: "Valentin Henriot"
date: "05/03/2020"
output: ioslides_presentation 
template: quarterly_report.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<style>
.html-widget {
    margin: auto;
}
</style>

## Sources used for the report

- Office fédéral statistique Suisse
- WDI
- Eurostat
- OECD
- spiR
- BIS
- Google Map
- opendata.swiss
- SKEMA Quantum Studio

## **Population map by canton**

```{r, include=FALSE}
library(sf)
library(ggplot2)
library(tmap)
library(tmaptools)
library(leaflet)
library(dplyr)
library(tidyr)
library(rdbnomics)
```

```{r, include=FALSE}
library(readxl)
CHdatamap <- read_excel("~/L3pgeprojects/CountryReportCH/MapCH/CHdatamap.xlsx", 
    sheet = "2018", col_types = c("text", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric"))
```

```{r, include=FALSE}
CHdatamap1 <- tidyr::drop_na(CHdatamap)
```

```{r, include=FALSE}
CHdatamap1 <- rename(CHdatamap1, NAME_1=...1)
```

```{r, include=FALSE}
CHdatamap2 <- ifelse(CHdatamap1$Total >= 1 & CHdatamap1$Total <= 50000, "1-50000", ifelse(CHdatamap1$Total >= 50001 & CHdatamap1$Total <= 100000, "50001-100000", ifelse(CHdatamap1$Total >= 100001 & CHdatamap1$Total <= 200000, "100001-200000", ifelse(CHdatamap1$Total >= 200001 & CHdatamap1$Total <= 300000, "200001-300000", ifelse(CHdatamap1$Total >= 300001 & CHdatamap1$Total <= 400000, "300001-400000", ifelse(CHdatamap1$Total >= 400001 & CHdatamap1$Total <= 500000, "400001-500000", ifelse(CHdatamap1$Total >= 500001 & CHdatamap1$Total <= 700000, "500001-700000", ifelse(CHdatamap1$Total >= 700001 & CHdatamap1$Total <= 1000000, "700001-1000000", ifelse(CHdatamap1$Total >= 1000000 & CHdatamap1$Total <= 1500000, "1000001-1500000", ifelse(CHdatamap1$Total >= 1500001, "1500000+", NA))))))))))
```

```{r, include=FALSE}
cut(CHdatamap1$Total, breaks=c(0, 50000, 100000, 200000, 300000, 400000, 500000, 700000, 1000000, 1500000, Inf), labels=c("0-50000", "50001-100000", "100001-200000", "200001-300000", "300001-400000", "400001-500000", "500001-700000", "700001-1000000", "1000001-1500000", "1500000+"))
```

```{r, include=FALSE}
mylabels <- c("0-50000", "50001-100000", "100001-200000", "200001-300000", "300001-400000", "400001-500000", "500001-700000", "700001-1000000", "1000001-1500000", "1500000+")
```

```{r, include=FALSE}
CHdatamap1$Population <- base::cut(CHdatamap1$Total,
                        breaks = c(0, 50000, 100000, 200000, 300000, 400000, 500000, 700000, 1000000, 1500000, 2000000), 
                        labels = mylabels, right = F, ordered_result = T)
```

```{r leaflet, message=FALSE, warning=FALSE, fig.align="center"}
myCHmap <- st_read("~/L3pgeprojects/CountryReportCH/MapCH/CHE_adm/CHE_adm1.shp", stringsAsFactors = FALSE)

datamap <- inner_join(myCHmap, CHdatamap1)

tm_shape(datamap) +
tm_polygons("Population", id = "NAME_1", palette = "Reds")+ 

tmap_mode("view")
DensityMap <- tmap_last()


tmap_save(DensityMap, "PopulationMapCH.html")
```

## **Analysis of the GDP growth in %**

```{r search indicator GDP, include=FALSE}
library(WDI)
CHGDP <-WDI(indicator = "NY.GDP.MKTP.KD.ZG",
country = c("CH"),
                   start = 1971,
                   end = 2018)
```

```{r delete iso2c column, include=FALSE}
CHGDP$iso2c <- NULL
```

```{r graphic about Switzerland GDP growth, fig.align='center'}
library(ggplot2)
 ggplot(CHGDP) +
 aes(x = year, y = NY.GDP.MKTP.KD.ZG) +
 geom_line(size = 1L, colour = "#0c4c8a") +
 labs(y = "Gdp growth in %", title = "Switzerland GDP growth in % (1971-2018)", caption = "Source: SKEMA Quantum Studio (WDI)") +
 theme_minimal()
```

```{r summary Switzerland GDP}
CHmeangdp <- summary(CHGDP$NY.GDP.MKTP.KD.ZG) 
CHmeangdp
```

## **GDP per capita**

```{r Compare countries GDP per capita, include=FALSE}
GdpPerCapitaComparison <- WDI(indicator = "NY.GDP.PCAP.PP.CD",
country = c("CH", "DE", "FRA", "IT"),
                   start = 1990,
                   end = 2018)
```

```{r Comparison graphic about GDP per capita, fig.align='center'}
ggplot(GdpPerCapitaComparison) +
 aes(x = year, y = NY.GDP.PCAP.PP.CD, colour = country) +
 geom_line(size = 1L) +
 scale_color_hue() +
 labs(y = "GDP per capita", title = "Comparison GDP per capita", caption = "Source: SKEMA Quantum Studio (WDI)") +
 theme_minimal()
```

## **Consumer Price Index**

The Consumer Price Index (CPI) is a measure of the average change over time in the prices paid by urban consumers for a market basket of consumer goods and services.

```{r Consumer Price Index, include=FALSE}
CPIc<- rdb(ids = c('BIS/long_cpi/A.CH.628', "BIS/long_cpi/A.FR.628", "BIS/long_cpi/A.IT.628", "BIS/long_cpi/A.DE.628")) %>%
  filter(!is.na(value))
CPIc <- rename(CPIc, Country = series_name) # Base 2010=100 (à inclure sur graphique)
```

```{r, fig.align='center'}
ggplot(CPIc, aes(x = period, y = value, color = Country)) +
  geom_line(size = 1) + 
  theme_dark() +
  theme(legend.position="bottom") + 
   guides(col = guide_legend(nrow = 4)) +
  labs(y = "Consumer Price Index", title = "CPI comparison", caption = "Source: SKEMA Quantum Studio (BIS)")
```

## **Comparison between imports and exports**

```{r Merchandise exports to high-income economies, include=FALSE}
CHExports <- WDI(indicator = "TX.VAL.MRCH.HI.ZS", #Merchandise exports to high-income economies (% of total merchandise exports)
country = c("CH"),
                   start = 1971,
                   end = 2018)
```

```{r Merchandise imports from low- and middle-income economies, include=FALSE}
CHImports <- WDI(indicator = "TM.VAL.MRCH.OR.ZS", #Merchandise imports from low- and middle-income economies outside region (% of total merchandise imports)
country = c("CH"),
                   start = 1971,
                   end = 2018)
```

```{r crossing board import export, include=FALSE}
library(dplyr)
ImportExport <- bind_cols(CHExports, CHImports)
```

```{r, include=FALSE}
base::colnames(ImportExport)[colnames(ImportExport)=="TX.VAL.MRCH.HI.ZS"] <- "ExportsToHighEconomies"
base::colnames(ImportExport)[colnames(ImportExport)=="TM.VAL.MRCH.OR.ZS"] <- "ImportsFromLowEconomies"
```


```{r, include=FALSE}
library(tidyr)

CHImportExport <- gather(data = ImportExport, key = TYPE, value = VAL, ExportsToHighEconomies, ImportsFromLowEconomies)
```

```{r Comparison graphic about imports and exports, fig.align='center'}
library(ggplot2)
ggplot(CHImportExport) +
 aes(x = year, y = VAL, colour = TYPE) +
 geom_line(size = 1L) +
  geom_vline(aes(xintercept = 2010), linetype=2, colour = "black", size = 1) +
  geom_vline(aes(xintercept = 2017), linetype=2, colour = "black", size = 1) +
 scale_color_hue() +
 labs(y = "In % of total trades", title = "Comparison about imports to high economies and 
      exports from low/middle economies ", caption = "Source: SKEMA Quantum Studio (WDI)") +
 theme_gray()
```

## **Balance of payments**

```{r, include=FALSE}
library(rdbnomics)
BalanceTransactionsC <- rdb(ids = c('AMECO/UBCA/CHE.1.0.0.0.UBCA', "AMECO/UBCA/FRA.1.0.0.0.UBCA", "AMECO/UBCA/ITA.1.0.0.0.UBCA", "AMECO/UBCA/DEU.1.0.0.0.UBCA")) %>%
  filter(!is.na(value))
BalanceTransactionsC <- rename(BalanceTransactionsC, country = series_name)
```

```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(plotly)
BalanceTransactionsCGraph <- ggplot(BalanceTransactionsC, aes(x = period, y = value, color = country)) +
  geom_line(size = 1) + 
  theme_dark() +
  theme(legend.position="bottom") + 
   guides(col = guide_legend(nrow = 4)) +
  labs(y = "Balance transaction", title = "Balance on current transactions with the rest of the world", caption = "Source: SKEMA Quantum Studio (AMECO)")

BalanceTransactionsCGraph <- ggplotly(BalanceTransactionsCGraph) %>%
  layout(legend = list(orientation = "h", x = 0.4, y = -0.2))
BalanceTransactionsC1 <- htmltools::div(BalanceTransactionsCGraph, align="center" )  # Result is now an HTML object
htmltools::save_html( BalanceTransactionsC1, "BalanceTransaction.html" )
BalanceTransactionsC1
```

## **How Switzerland deals with unemployement?**

```{r Unemployment with advanced education comparison, include=FALSE}
UAEcomparison<- WDI(indicator = "SL.UEM.ADVN.ZS", #Unemployment with advanced education (% of total labor force with advanced education)
country = c("CH", "DE", "FRA", "IT"),
                   start = 2000,
                   end = 2018)
```

```{r Renaming column Advanced_Education comparison, include=FALSE}
base::colnames(UAEcomparison)[colnames(UAEcomparison)=="SL.UEM.ADVN.ZS"] <- "Advanced_EducationC"
```

```{r Unemployment intermediate education comparison, include=FALSE}
UIEcomparison<- WDI(indicator = "SL.UEM.INTM.ZS", #Unemployment with intermediate education (% of total labor force with advanced education)
country = c("CH", "DE", "FRA", "IT"),
                   start = 2000,
                   end = 2018)
```

```{r Renaming column Intermediate_Education comparison, include=FALSE}
base::colnames(UIEcomparison)[colnames(UIEcomparison)=="SL.UEM.INTM.ZS"] <- "Intermediate_EducationC"
```

```{r Unemployment basic education comparison, include=FALSE}
UBEcomparison <- WDI(indicator = "SL.UEM.BASC.ZS", #Unemployment with basic education (% of total labor force with advanced education)
country = c("CH", "DE", "FRA", "IT"),
                   start = 2000,
                   end = 2018)
```

```{r Renaming column Basic_Education comparison, include=FALSE}
base::colnames(UBEcomparison)[colnames(UBEcomparison)=="SL.UEM.BASC.ZS"] <- "Basic_EducationC"
```

```{r Combining columns comparison, include=FALSE}
library(dplyr)
UCjoin <- bind_cols(UAEcomparison, UIEcomparison, UBEcomparison)
```

```{r Delete some columns comparison, include=FALSE}
UCjoin$iso2c <- NULL
UCjoin$iso2c1 <- NULL
UCjoin$country1 <- NULL
UCjoin$year1 <- NULL
UCjoin$iso2c2 <- NULL
UCjoin$country2 <- NULL
UCjoin$year2 <- NULL
```

```{r Re-arrange columns comparison, include=FALSE}
UCjoin <- UCjoin[c(1,3,2,4,5)]
```

```{r Gather data about unemployment comparison, include=FALSE}
library(tidyr)

UCjoinTest <- gather(data = UCjoin, key = TYPE, value = VAL, Advanced_EducationC, Intermediate_EducationC, Basic_EducationC)
```

```{r Graphic about unemployment rate by education level comparison, fig.align='center'}
qplot(data = UCjoinTest, y = VAL, x = year, color = TYPE, geom = "line") + 
  labs(y = "Unemployment rate in %", title = "Unemployment rate by education level", caption = "Source: SKEMA Quantum Studio (WDI)") +
  facet_wrap(~ country) +
  theme_linedraw()
```

## **Social progress index**

“The Social Progress Index is a new way to define the success of our societies. It is a comprehensive measure of real quality of life, independent of economic indicators.” (The Social Progress Imperative, 2018)

```{r Library call, include=FALSE}
library(spiR)
library(kableExtra)
library(ggplot2)
library(dplyr)
```

```{r Generate SPI data, include=FALSE}
SPIc <- sqs_spi_data(country = c("CHE", "FRA", "DEU", "ITA"), 
                       year = c("2014","2015","2016", "2017", "2018", "2019"), 
                       indicators = "SPI")
```

```{r Convert value to numeric SPI, include=FALSE}
SPIc$value <- as.numeric(SPIc$value)
```

```{r Generate new board SPI, include=FALSE}
kable(SPIc)%>%
scroll_box(width = "100%", height = "200px")
```

```{r Generate SPI graphic, fig.align='center'}
ggplot(data = SPIc, aes(x = var_year, y = value, color = countryName)) + 
  geom_line() +
  theme_grey() +
  theme(plot.title = element_text(hjust = 0.5)) + 
  labs(title = "Social Progress Index of 4 different european countries since 2014",
       x = "Years",
       y = "Social Progress Index Score",
       colour = "Countries",
       caption = "Source: SKEMA Quantum Studio (spiR)")
```

## **Expenditure on education**

```{r, include=FALSE}
ExpenditureEducationC <- WDI(indicator = "SE.XPD.TOTL.GD.ZS", #Government expenditure on education, total (% of GDP)
country = c("CH", "FRA", "DE", "ITA"),
                   start = 1996,
                   end = 2016)
ExpenditureEducationC <- dplyr::rename(ExpenditureEducationC, Government_Expenditure = SE.XPD.TOTL.GD.ZS)
```

```{r, include=FALSE}
GDPComparison <- WDI(indicator = "NY.GDP.MKTP.CD", #GDP
country = c("CH", "FRA", "DE", "ITA"),
                   start = 1996,
                   end = 2016)
GDPComparison <- dplyr::rename(GDPComparison, GDP = NY.GDP.MKTP.CD)
```

```{r, include=FALSE}
library(dplyr)
PlotEducationGDP <- bind_cols(ExpenditureEducationC, GDPComparison)
```

```{r message=FALSE, warning=FALSE}
library(plotly)
DynGraphPlotEducationGDP <- ggplot(PlotEducationGDP, aes(year, Government_Expenditure, color = country)) +
  geom_point(aes(size = GDP, frame = year)) +
  scale_x_log10() +
  hrbrthemes::theme_modern_rc() +
  labs(y = "Government Expenditure in % of GDP", title = "Expenditure on education in % of GDP")
DynGraphPlotEducationGDP <- ggplotly(DynGraphPlotEducationGDP)
DynGraphPlotEducationGDP 
```

## **Foreign population**

```{r, include=FALSE}
ForeignPopulation <- rdb(ids = c('OECD/MIG/TOTP.B15.TOT.CHE', "OECD/MIG/TOTP.B15.TOT.FRA", "OECD/MIG/TOTP.B15.TOT.ITA", "OECD/MIG/TOTP.B15.TOT.DEU")) %>%
  filter(!is.na(value))
```

```{r, include=FALSE}
ForeignPopulationPlot <- ggplot(ForeignPopulation, aes(x = period, y = value, color = Country)) +
  geom_line(size = 1) + 
  theme_light() +
  theme(legend.position="bottom") + 
   guides(col = guide_legend(nrow = 4)) +
  labs(y = "Foreign population in % of total pop", title = "Stock of foreign population by nationality", caption = "Source: SKEMA Quantum Studio (OECD)")
```

```{r, include=FALSE}
library(grid)
my_text <- "Huge gap between Switzerland
and Germany"
my_grob = grid.text(my_text, x=0.7,  y=0.6, gp=gpar(col="black", fontsize=12, fontface="bold"))
```

```{r, fig.align='center'}
ForeignPopulationPlot + annotation_custom(my_grob)
```

## **Intentional homicide ratio**

```{r, include=FALSE}
CrimesComparison <- rdb(ids = c('Eurostat/crim_hom_soff/A.ICCS0101.PER_CNV.T.P_HTHAB.CH', "Eurostat/crim_hom_soff/A.ICCS0101.PER_CNV.T.P_HTHAB.FR", "Eurostat/crim_hom_soff/A.ICCS0101.PER_CNV.T.P_HTHAB.IT", "Eurostat/crim_hom_soff/A.ICCS0101.PER_CNV.T.P_HTHAB.DE")) %>%
  filter(!is.na(value))
CrimesComparison
```

```{r, include=FALSE}
base::colnames(CrimesComparison)[colnames(CrimesComparison)=="Geopolitical entity (reporting)"] <- "Country" 
```

```{r, include=FALSE}
CrimesComparisonPlot <- ggplot(CrimesComparison, aes(x = period, y = value, color = Country)) +
  geom_line(size = 1) + 
  theme_gray() +
  theme(legend.position="bottom") + 
   guides(col = guide_legend(nrow = 4)) +
  labs(y = "Intentional homicide per 
       hundred thousand inhabitants", title = "Crimes stats", caption = "Source: SKEMA Quantum Studio (Eurostat)")
```

```{r, fig.align='center'}
CrimesComparisonPlot + theme(plot.title=element_text(size=20, 
                                    face="bold", 
                                    family="American Typewriter",
                                    color="#E81232",
                                    hjust=0.5,
                                    lineheight=1.2))
```

## **Risk of poverty or social exclusion**

In 2017, 112.8 million people in the EU lived in households at risk of poverty or social exclusion; 22.4 % of the population. **(Eurostat)**

```{r, include=FALSE}
PovertyComparison <- rdb(ids = c('Eurostat/ilc_peps01/A.PC.TOTAL.T.CH', "Eurostat/ilc_peps01/A.PC.TOTAL.T.IT", "Eurostat/ilc_peps01/A.PC.TOTAL.T.FR", "Eurostat/ilc_peps01/A.PC.TOTAL.T.DE")) %>%
  filter(!is.na(value))
```

```{r, include=FALSE}
base::colnames(PovertyComparison)[colnames(PovertyComparison)=="Geopolitical entity (reporting)"] <- "Country" 
```

```{r, fig.align='center'}
ggplot(PovertyComparison, aes(x = period, y = value, color = Country)) +
  geom_line(size = 1) + 
  theme_gray() +
  theme(legend.position="bottom") + 
   guides(col = guide_legend(nrow = 4)) +
  labs(y = "% at risk of poverty", title = "People at risk of poverty or social exclusion",      caption = "Source: SKEMA Quantum Studio (Eurostat)") +
  ggthemes::theme_stata()
```

## **Corruption Perceptions Index**

A score of 0 representing a very high level of corruption and a score of 100 representing a very clean country.

```{r include=FALSE}
CorruptionIndex <- rdb(ids = c('Eurostat/sdg_16_50/A.NR.CH', "Eurostat/sdg_16_50/A.NR.FR", "Eurostat/sdg_16_50/A.NR.IT", "Eurostat/sdg_16_50/A.NR.DE")) %>%
  filter(!is.na(value))
```

```{r include=FALSE}
CorruptionIndex2019 <- filter(CorruptionIndex, original_period == 2019)
```

```{r include=FALSE}
base::colnames(CorruptionIndex2019)[colnames(CorruptionIndex2019)=="Geopolitical entity (reporting)"] <- "Country" 
```

```{r}
## Recoding CorruptionIndex2019$Country
CorruptionIndex2019$Country <- recode(CorruptionIndex2019$Country,
               "Germany (until 1990 former territory of the FRG)" = "Germany")
```

```{r, fig.align='center'}
ggplot(CorruptionIndex2019) +
 aes(x = Country, colour = Country, weight = value) +
 geom_bar(fill = "#0c4c8a") +
 scale_color_hue() +
 labs(y = "Value", title = "Corruption Perceptions Index", caption = "Source: SKEMA Quantum Studio (Eurostat)") +
 ggthemes::theme_stata()
```

## **Swiss industries**

```{r}
IndustryCH <- data.frame(Industry=c("Primary_Sector", "Secondary-Sector", "Tertiary_Sector"), NumberOfCompanies=c(8.98, 15.33, 75.69)) ## Office fédéral statistique Suisse, data 2017
IndustryCH$Industry <- as.character(IndustryCH$Industry)
```

```{r, fig.align='center'}
pie = ggplot(IndustryCH, aes(x="", y=NumberOfCompanies, fill=Industry)) + geom_bar(stat="identity", width=1)
 
pie = pie + coord_polar("y", start=0) + geom_text(aes(label = paste0(round(NumberOfCompanies), "%")), position = position_stack(vjust = 0.5))
 
pie = pie + scale_fill_manual(values=c("#C77528", "#F09F27", "#3E7AC9")) 
 
pie = pie + labs(x = NULL, y = NULL, fill = NULL, title = "Switzerland Industries", caption = "Source: SKEMA Quantum Studio (Office fédéral statistique Suisse)")
 
pie = pie + theme_classic() + theme(axis.line = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(hjust = 0.5, color = "black"))
pie
```